---
title: "Eating Out"
author: "Elizabeth Rivera"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out.


Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```

link to the NORC site; get the data here
https://gssdataexplorer.norc.org/variables/vfilter


```{r, eval=T}
GSS <-read.dta(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


```{r}
barchartGC(~race+eatout,data=mydata, type="percent")
```

Among the races it demonstrates they all eat out. The white race eats out the most among all races and the black race eats out the least among all races. The other race is between the white and black race.   


## Numerical Description  

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

Among the white race 82% eat out and 17% don't eat out. Among the black race 68% eat out while 31% don't. Among the other race 77% eat out and 22% don't. 

## Inferential Description  

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

Chi squared test has a p-value of 0.0008179 which is less than 0.05 so we reject the null hypothesis. This means there is a difference in the frequency of eating out among the races.   


```{r}
fisherXY(mydata$race,mydata$eatout)
```



## Conclusion  

